Reassessing the cost-effectiveness of pneumococcal conjugate vaccines in low- and middle-income countries using opportunity cost-based thresholds

### 2024-08-01 manuscript.tex
Updates from Overleaf

\subsection{Factors associated with switching from cost-effective to not cost-effective}
[In progress]
Descriptively, evaluations that switched from being cost-effective to not cost-effective under any of the updated CETs were more likely to be comparisons between PCV7 versus no vaccination or PCV10 versus no vaccination. They were also more likely to be conducted in lower income settings, not to consider herd immunity, but to consider serotype replacement . None of these associations were statistically significant according to the Pearson Chi squared test. No relationship was found between perspective of analysis and the evaluation switching from begin cost-effective. However, evaluations that switched from being cost-effective to not cost-effective across any of the new CETs had statistically higher mean vaccine dose price: \$31.82 (\$26.73-\$36.91) vs \$15.41 (\$7.26-\$23.55).  Probit regression results found vaccine dose price and country income group were the only statistically significant variables related to evaluations switching from being cost-effective to not cost-effective across any one of the updated CETs.

\begin{table}[H]
    \centering \singlespacing \small
    \caption{Characteristics of included evaluations and unique studies}
    \begin{tabular}{|L{4.5cm}|L{4cm}|C{2.75cm}|C{2.75cm}|}
        \hline
        \PlainInput{tables/tab_likely_anyswitch}
    \end{tabular}
    \label{tab_likely_anyswitch}
    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7. \\
    IPD, invasive pneumococcal disease; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV. 
}
\end{table}

>>>>

\subsection{Factors associated with switching from cost-effective to not cost-effective}
[In progress]
Descriptively, evaluations that switched from being cost-effective to not cost-effective under any of the updated CETs were more likely to be comparisons between PCV7 versus no vaccination or PCV10 versus no vaccination. They were also more likely to be conducted in lower income settings, not to consider herd immunity, but to consider serotype replacement . None of these associations were statistically significant according to the Pearson Chi squared test. No relationship was found between perspective of analysis and the evaluation switching from begin cost-effective. However, evaluations that switched from being cost-effective to not cost-effective across any of the new CETs had statistically higher mean vaccine dose price: \$27.7  vs \$15.5 (mean difference \$12.2, 95\% confidence interval, 2.9 to 21.4).

Probit regression results found vaccine dose price and country income group were the only statistically significant variables related to evaluations switching from being cost-effective to not cost-effective across any one of the updated CETs.

\begin{table}[H]
    \centering \singlespacing \small
    \caption{Likelihood of switching}
    \begin{tabular}{|L{4.5cm}|L{4cm}|C{2.75cm}|C{2.75cm}|}
        \hline
        \PlainInput{tables/tab_likely_anyswitch}
    \end{tabular}
    \label{tab_likely_anyswitch}
    \caption*{\footnotesize \textit{Notes:} Other evaluations included PCV9 vs NoVax, PCV13 vs PCV7, and PCV10 vs PCV7. \\
    IPD, invasive pneumococcal disease; PCV, pneumococcal conjugate vaccine; PCV7, 7-valent PCV; PCV10, 10-valent PCV; PCV13, 13-valent PCV. 
}
\end{table}
